Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-02-24 WSSSPE2_report/WSSSPE2_review.tex
Use href command for external links to google docs notes
The string "google doc notes" can be clicked to open the corresponding
section of the document in a browser

Google doc notes - \url{http://tinyurl.com/mpbhvyb}
%https://docs.google.com/a/uchicago.edu/document/d/10XkshP3YjXnA5JQgP-UFHbOxshWczzehWGSo6V7bNH4/edit

@@

Google doc notes - \url{http://tinyurl.com/pn4eq8z}
%https://docs.google.com/a/uchicago.edu/document/d/1_q0jmiEPNFRGAEtGLk_QxQ1vVokgTDYruTGURowNGkY/edit

@@

Google doc notes - \url{http://tinyurl.com/k8ruyn9}
%https://docs.google.com/document/d/1Jsi_trBT5cjEXVnGjGHJpcIhMEcVpAn6XmYNxfIHXv0/edit#heading=h.gk1dzxu9wi6q

@@

Google doc notes - 
\href{http://tinyurl.com/kqpe87z}
%https://docs.google.com/document/d/1Mivadj16_9tPrw8Nxmhp72AtNC0BEVO-f7M84FXTbSU/edit#heading=h.elaktnt2tep9

@@

Google doc notes - 
\url{http://tinyurl.com/l5t5h45}
%https://docs.google.com/document/d/1G1_U5-hkAvDKtTgT4DvUhIYvyYUY4cBBvQHJIdgADa0/edit#heading=h.v7g0nqpn1fur

>>>>

\href{http://tinyurl.com/mpbhvyb}{Google doc notes}
%https://docs.google.com/a/uchicago.edu/document/d/10XkshP3YjXnA5JQgP-UFHbOxshWczzehWGSo6V7bNH4/edit

@@

\href{http://tinyurl.com/pn4eq8z}{Google doc notes}
%https://docs.google.com/a/uchicago.edu/document/d/1_q0jmiEPNFRGAEtGLk_QxQ1vVokgTDYruTGURowNGkY/edit

@@

\href{http://tinyurl.com/k8ruyn9}{Google doc notes}
%https://docs.google.com/document/d/1Jsi_trBT5cjEXVnGjGHJpcIhMEcVpAn6XmYNxfIHXv0/edit#heading=h.gk1dzxu9wi6q

@@

\href{http://tinyurl.com/kqpe87z}{Google doc notes}
%https://docs.google.com/document/d/1Mivadj16_9tPrw8Nxmhp72AtNC0BEVO-f7M84FXTbSU/edit#heading=h.elaktnt2tep9

@@

\href{http://tinyurl.com/l5t5h45}{Google doc notes}
%https://docs.google.com/document/d/1G1_U5-hkAvDKtTgT4DvUhIYvyYUY4cBBvQHJIdgADa0/edit#heading=h.v7g0nqpn1fur
